---
title: "Rejection Sample Package"
author: "Youssef Younis <youssef.younis@slu.edu>"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

When working with this package you must:

- Provide either a Probability Density Function or a Joint Density Function
- Provide Upper and Lower Boundaries of each of your specific variables and either your Probability Density Function or Join Density Function
- Provide Upper and Lower Boundaries for your desired Probabilities

The Rejection Sample Package calculates you the following:

- Sample from $X$ given its probability density function
- Sample from ($X$,$Y$) given the joint density function
- Compute the expected value of $f(X)$ or $f(X,Y)$ given a function $f()$.
- Compute probabilities related to $X$ or $X$ and $Y$.

This package was developed as a optional project for a required Probability Theory course 4800 Probability Theory. This course is taught at Saint Louis University by Dr. Darren Speegle <speegled@slu.edu>.


##Section A) Sample from $X$ given its probability density function

The initial section to the project focuses on receiving a random sample from a probability density function utilizing rejection sampling. Here you must provide us with the following parameters:

- The probability density function for your desired variable
- The upper and lower bounds of your probability density function

```{r}
set.seed(123)
library(dplyr)
gx <- function(x){return(4*x)}
SpecificSample <- mutate(data.frame( x = seq(0, sqrt(.5), .01)), y = gx(x))
max_c(0, sqrt(.5), y = 4*x)
```

Here the function provided calculates the maximum value that is set higher than the maximum value of the probability.

```{r}
ApproveReject(0, sqrt(.5), y = gx(x))
```

```{r}
head(Replication(0, sqrt(.5), y = gx(x))) %>% rename("Random Sample" = "x")
```

The utilization of head allows you to take the first few samples after replication. 

##Section B) Sample from ($X$,$Y$) given the joint density function

The second section of this project focuses on receiving a random sample from a joint density function. Here you must provide the following:

  - The joint density function for your desired variables
  - The upper and lower boundaries for your joint density functions and variables
  
```{r}
gx = function(x,y){
return (x+y)}
head(SampleJDF(0, 0, 1, 1, 0, 2, gx)) %>% rename("Random Sample X-Coordinate" = "x", "Random Sample Y-Coordinate" = "y")
```

The utilization of head allows you to take the first few samples after replication. 

##Section C) Compute the expected value of $f(X)$ or $f(X,Y)$ given a function $f()$.

The third section of the project focuses on producing an expected outcome for either a probability density function or a joint density function. Here you must provide us with the following parameters:

- 
