---
title: "Rejection Sample Package"
author: "Youssef Younis <youssef.younis@slu.edu>"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

When working with this package you must:

- Provide either a Probability Density Function or a Joint Density Function
- Provide Upper and Lower Boundaries of each of your specific variables and either your Probability Density Function or Join Density Function
- Provide Upper and Lower Boundaries for your desired Probabilities

The Rejection Sample Package calculates you the following:

- Sample from $X$ given its probability density function
- Sample from ($X$,$Y$) given the joint density function
- Compute the expected value of $f(X)$ or $f(X,Y)$ given a function $f()$.
- Compute probabilities related to $X$ or $X$ and $Y$.

This package was developed as a optional project for a required Probability Theory course 4800 Probability Theory. This course is taught at Saint Louis University by Dr. Darren Speegle <speegled@slu.edu>.


##Section A) Sample from $X$ given its probability density function

The initial section to the project focuses on receiving a random sample from a probability density function utilizing rejection sampling. Here you must provide us with the following parameters:

- The probability density function for your desired variable
- The upper and lower bounds of your probability density function

```{r}
set.seed(123)
library(dplyr)
gx <- function(x){return(4*x)}
SpecificSample <- mutate(data.frame( x = seq(0, sqrt(.5), .01)), y = gx(x))
max_c(0, sqrt(.5), y = 4*x)
```

Here the function provided calculates the maximum value that is set higher than the maximum value of the probability.

```{r}
ApproveReject(0, sqrt(.5), y = gx(x))
```

```{r}
head(Replication(0, sqrt(.5), y = gx(x))) %>% rename("Random Sample" = "x")
```

The utilization of head allows you to take the first few samples after replication. 
## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
