---
title: "Rejection Sample Package"
author: "Youssef Younis <youssef.younis@slu.edu>"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

When working with this package you must:

- Provide either a Probability Density Function or a Joint Density Function
- Provide Upper and Lower Boundaries of each of your specific variables and either your Probability Density Function or Join Density Function
- Provide Upper and Lower Boundaries for your desired Probabilities

The Rejection Sample Package calculates you the following:

- Sample from $X$ given its probability density function
- Sample from ($X$,$Y$) given the joint density function
- Compute the expected value of $f(X)$ or $f(X,Y)$ given a function $f()$.
- Compute probabilities related to $X$ or $X$ and $Y$.

This package was developed as a optional project for a required Probability Theory course 4800 Probability Theory. This course is taught at Saint Louis University by Dr. Darren Speegle <speegled@slu.edu>.

##Installation of Package

```{r}
library(Project4800)
```


##Section A) Sample from $X$ given its probability density function

The initial section to the project focuses on receiving a random sample from a probability density function utilizing rejection sampling. Here you must provide us with the following parameters:

- The probability density function for your desired variable
- The upper and lower bounds of your probability density function

```{r, include=FALSE}
set.seed(123)
suppressMessages(library(dplyr))
suppressMessages(library(Project4800))
gx <- function(x){return(4*x)}
SpecificSample <- mutate(data.frame( x = seq(0, sqrt(.5), .01)), y = gx(x))
max_c(0, sqrt(.5), y = 4*x)
```

Here the function provided calculates the maximum value that is set higher than the maximum value of the probability.

```{r}
ApproveReject(0, sqrt(.5), y = gx(x))
```

```{r}
head(Replication(0, sqrt(.5), y = gx(x))) %>% rename("Random Sample" = "x")
```

The utilization of head allows you to take the first few samples after replication. 

##Section B) Sample from ($X$,$Y$) given the joint density function

The second section of this project focuses on receiving a random sample from a joint density function. Here you must provide the following:

  - The joint density function for your desired variables
  - The upper and lower boundaries for your joint density functions and variables
  
```{r}
gx = function(x,y){
return (x+y)}
head(SampleJDF(0, 0, 1, 1, 0, 2, gx)) %>% rename("Random Sample X-Coordinate" = "x", "Random Sample Y-Coordinate" = "y")
```

The utilization of head allows you to take the first few samples after replication. 

##Section C) Compute the expected value of $f(X)$ or $f(X,Y)$ given a function $f()$.

The third section of the project focuses on producing an expected outcome for either a probability density function or a joint density function. Here you must provide us with the following parameters:

- User provided joint density function or probability function
- Desired Variables whether it be the character of $X$ or $XY$
- Upper and lower boundaries for provided function and variables
- Numerical Value for desired amount of replication

```{r}
f = function(x) {return(2*x)}
ExpectedValue(f, "X", lower_boundx = 0, upper_boundx = 1)
```

The provided example above demonstrates the expected outcome for a probabilty density function with the desired variable $x$.

```{r}
f = function(x) {return(1/2/pi *(sin(x) + 1))}
ExpectedValue(f, "X", lower_boundx = 0, upper_boundx = 2* pi)
```

The example above is similar to the first example provided in this section; however, it demonstrates computing an expected value with a sin function.

```{r}
f = function(x,y) {return(x+y)}
ExpectedValue(f, variable = "XY", upper_boundx = 1, upper_boundy = 1, upper_boundF = 2, lower_boundx = 0, lower_boundy = 0, lower_boundF = 0)
```

The final example provided shows the function computing the expected outcome for a joint density function.

##Section D) Compute probabilities related to $X$ or $X$ and $Y$.

The final section of the project focuses on producing probabilities given a probability density function or a joint density function. Here you must provide us with the following paramaters:

- User provided joint density function or probability function
- Desired Variables whether it be the character of $X$ or $XY$
- Upper and lower boundaries for provided function, variables, and probability
- Numerical Value for desired amount of replication

```{r}
f = function(x) {return(4*x)}
Prob(f, variable = "X", upper_boundx = .5, upper_boundP = .3, lower_boundx = 0, lower_boundP = 0, Rep = 10000)
```

The provided example above shows a basic probability computation with given boundaries, varible, replication, and probability density function.

```{r}
f = function(x) {return(1/2/pi *(sin(x) + 1))}
Prob(f, variable = "X", upper_boundx = 2*pi, lower_boundP = pi, lower_boundx = 0, Rep = 10000)
```

The provided example above shows another probability computation; however, it demonstrates computating a probability with a sin function.

